---
title: "RQ3. Economic Left-Right Saliency Moderation"
output: 
  html_document: 
    toc: yes
    keep_md: yes
date: '`r Sys.Date()`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

RQ3. If, as expected (H2), some personal values are associated with the Economic Left-Right position of the party for which one has voted, are those associations stronger if this dimension is salient in the party’s public stance (i.e., is there a boundary condition to these associations, such that the ideology needs to be salient in order for the associations to exist)?
H5. We expect the associations between personal values and Economic Left-Right to be stronger if this dimension is salient in the party’s public stance.

H2 confirmed association for universalism and power values.


# Preparations

## Packages

```{r}

library(lme4)
library(lmerTest)
library(emmeans)
library(r2mlm)
library(rio)
library(dplyr)
library(vjihelpers)
library(psych)
library(tibble)

```

## Functions

```{r}

source("../custom_functions.R")
```

## Data

```{r}
fdat<-import("../../data/processed/fdat.xlsx")
```

## Variables

```{r}

value.vars<-
  c("con","tra","ben","uni","sdi",
        "sti","hed","ach","pow","sec")

value.vars.c<-paste0(value.vars,".c")

DV.vars<-names(fdat)[which(names(fdat)=="lrgen.z"):
                       which(names(fdat)=="corrupt_salience.z")]

```

## Data filtering and centering predictors

```{r}

temp.fdat<- fdat %>% 
    dplyr::select(all_of(value.vars),
                  all_of(value.vars.c),
                  "lrecon.z",
                  "lrecon_salience.z",
                  "gndr.c",
                  "age10.c",
                  "cntry",
                  "anweight") %>%
    na.omit()

temp.fdat<-
    group_mean_center(data=temp.fdat,group.var = "cntry",
                      vars = c(value.vars,
                               value.vars.c,
                               "lrecon_salience.z",
                               "gndr.c",
                               "age10.c"))
```

# Analysis

## uni

### fixed effect model

```{r}
mod2.uni<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+uni.c.gmc+(1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod2.uni)
```

### salience main effect

```{r}
mod3.uni<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+uni.c.gmc+
                 lrecon_salience.z.gmc+
             (1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod3.uni)
```

### salience moderation

```{r}
mod4.uni<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+uni.c.gmc+
                 lrecon_salience.z.gmc+
             uni.c.gmc:lrecon_salience.z.gmc+
             (1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod4.uni)

emtrends(mod4.uni,
         var="uni.c.gmc",
         specs="lrecon_salience.z.gmc",
         at=list(lrecon_salience.z.gmc=c(-1,0,1)),
         disable.pbkrtest=T,
         lmerTest.limit = 25000,
         infer=c(T,T))

```

### figure data

```{r}
by=0.05

p.uni<-
  emmip(mod4.uni,
        lrecon_salience.z.gmc ~ uni.c.gmc,
        at=list(lrecon_salience.z.gmc = c(-1,0,1),
                uni.c.gmc=
                  seq(from=
                        round(range(temp.fdat$uni.c.gmc)[1],2),
                      to=round(range(temp.fdat$uni.c.gmc)[2],
                               2),by=by)),
        plotit=F,CIs=TRUE,type="response",
        disable.pbkrtest=T,lmerTest.limit=30000)

p.uni$lrecon_salience<-p.uni$tvar

levels(p.uni$lrecon_salience)<-
  c("Low Salience","Average Salience","High Salience")

min.low<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc<=(-1),
                "uni.c.gmc"])
max.low<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc<=(-1),
                "uni.c.gmc"])

p.uni$filter.low<-
  ifelse(p.uni$lrecon_salience.z.gmc==(-1) &
           (p.uni$uni.c.gmc<min.low | 
              p.uni$uni.c.gmc>max.low),0,1)

table(p.uni$filter.low)

min.mid<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc>(-1) |
                  temp.fdat$lrecon_salience.z.gmc<(1),
                "uni.c.gmc"])
max.mid<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc>(-1) |
                  temp.fdat$lrecon_salience.z.gmc<(1),
                "uni.c.gmc"])

p.uni$filter.mid<-
  ifelse(p.uni$lrecon_salience.z.gmc==(0) &
           (p.uni$uni.c.gmc<min.mid | 
              p.uni$uni.c.gmc>max.mid),0,1)

table(p.uni$filter.mid)

min.high<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc>=(1) ,
                "uni.c.gmc"])
max.high<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc>=(1) ,
                "uni.c.gmc"])

p.uni$filter.high<-
  ifelse(p.uni$lrecon_salience.z.gmc==(1) &
           (p.uni$uni.c.gmc<min.high | 
              p.uni$uni.c.gmc>max.high),0,1)

table(p.uni$filter.high)

export(p.uni,overwrite=T,
       "../../results/figures/figdata/uni_ELR_salience.xlsx")

```

## pow

### fixed effect model

```{r}
mod2.pow<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+pow.c.gmc+(1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod2.pow)
```

### salience main effect

```{r}
mod3.pow<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+pow.c.gmc+
                 lrecon_salience.z.gmc+
             (1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod3.pow)
```

### salience moderation

```{r}
mod4.pow<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+pow.c.gmc+
                 lrecon_salience.z.gmc+
             pow.c.gmc:lrecon_salience.z.gmc+
             (1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod4.pow)

emtrends(mod4.pow,
         var="pow.c.gmc",
         specs="lrecon_salience.z.gmc",
         at=list(lrecon_salience.z.gmc=c(-1,0,1)),
         disable.pbkrtest=T,
         lmerTest.limit = 25000,
         infer=c(T,T))


```

### figure data

```{r}
by=0.05

p.pow<-
  emmip(mod4.pow,
        lrecon_salience.z.gmc ~ pow.c.gmc,
        at=list(lrecon_salience.z.gmc = c(-1,0,1),
                pow.c.gmc=
                  seq(from=
                        round(range(temp.fdat$pow.c.gmc)[1],2),
                      to=round(range(temp.fdat$pow.c.gmc)[2],
                               2),by=by)),
        plotit=F,CIs=TRUE,type="response",
        disable.pbkrtest=T,lmerTest.limit=30000)

p.pow$lrecon_salience<-p.pow$tvar

levels(p.pow$lrecon_salience)<-
  c("Low Salience","Average Salience","High Salience")

min.low<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc<=(-1),
                "pow.c.gmc"])
max.low<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc<=(-1),
                "pow.c.gmc"])

p.pow$filter.low<-
  ifelse(p.pow$lrecon_salience.z.gmc==(-1) &
           (p.pow$pow.c.gmc<min.low | 
              p.pow$pow.c.gmc>max.low),0,1)

table(p.pow$filter.low)

min.mid<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc>(-1) |
                  temp.fdat$lrecon_salience.z.gmc<(1),
                "pow.c.gmc"])
max.mid<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc>(-1) |
                  temp.fdat$lrecon_salience.z.gmc<(1),
                "pow.c.gmc"])

p.pow$filter.mid<-
  ifelse(p.pow$lrecon_salience.z.gmc==(0) &
           (p.pow$pow.c.gmc<min.mid | 
              p.pow$pow.c.gmc>max.mid),0,1)

table(p.pow$filter.mid)

min.high<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc>=(1) ,
                "pow.c.gmc"])
max.high<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc>=(1) ,
                "pow.c.gmc"])

p.pow$filter.high<-
  ifelse(p.pow$lrecon_salience.z.gmc==(1) &
           (p.pow$pow.c.gmc<min.high | 
              p.pow$pow.c.gmc>max.high),0,1)

table(p.pow$filter.high)

export(p.pow,overwrite=T,
       "../../results/figures/figdata/pow_ELR_salience.xlsx")

```

## ben

### fixed effect model

```{r}
mod2.ben<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+ben.c.gmc+(1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod2.ben)
```

### salience main effect

```{r}
mod3.ben<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+ben.c.gmc+
                 lrecon_salience.z.gmc+
             (1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod3.ben)
```

### salience moderation

```{r}
mod4.ben<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+ben.c.gmc+
                 lrecon_salience.z.gmc+
             ben.c.gmc:lrecon_salience.z.gmc+
             (1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod4.ben)

emtrends(mod4.ben,
         var="ben.c.gmc",
         specs="lrecon_salience.z.gmc",
         at=list(lrecon_salience.z.gmc=c(-1,0,1)),
         disable.pbkrtest=T,
         lmerTest.limit = 25000,
         infer=c(T,T))

```

### figure data

```{r}
by=0.05

p.ben<-
  emmip(mod4.ben,
        lrecon_salience.z.gmc ~ ben.c.gmc,
        at=list(lrecon_salience.z.gmc = c(-1,0,1),
                ben.c.gmc=
                  seq(from=
                        round(range(temp.fdat$ben.c.gmc)[1],2),
                      to=round(range(temp.fdat$ben.c.gmc)[2],
                               2),by=by)),
        plotit=F,CIs=TRUE,type="response",
        disable.pbkrtest=T,lmerTest.limit=30000)

p.ben$lrecon_salience<-p.ben$tvar

levels(p.ben$lrecon_salience)<-
  c("Low Salience","Average Salience","High Salience")

min.low<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc<=(-1),
                "ben.c.gmc"])
max.low<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc<=(-1),
                "ben.c.gmc"])

p.ben$filter.low<-
  ifelse(p.ben$lrecon_salience.z.gmc==(-1) &
           (p.ben$ben.c.gmc<min.low | 
              p.ben$ben.c.gmc>max.low),0,1)

table(p.ben$filter.low)

min.mid<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc>(-1) |
                  temp.fdat$lrecon_salience.z.gmc<(1),
                "ben.c.gmc"])
max.mid<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc>(-1) |
                  temp.fdat$lrecon_salience.z.gmc<(1),
                "ben.c.gmc"])

p.ben$filter.mid<-
  ifelse(p.ben$lrecon_salience.z.gmc==(0) &
           (p.ben$ben.c.gmc<min.mid | 
              p.ben$ben.c.gmc>max.mid),0,1)

table(p.ben$filter.mid)

min.high<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc>=(1) ,
                "ben.c.gmc"])
max.high<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc>=(1) ,
                "ben.c.gmc"])

p.ben$filter.high<-
  ifelse(p.ben$lrecon_salience.z.gmc==(1) &
           (p.ben$ben.c.gmc<min.high | 
              p.ben$ben.c.gmc>max.high),0,1)

table(p.ben$filter.high)

export(p.ben,overwrite=T,
       "../../results/figures/figdata/ben_ELR_salience.xlsx")

```

## ach

### fixed effect model

```{r}
mod2.ach<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+ach.c.gmc+(1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod2.ach)
```

### salience main effect

```{r}
mod3.ach<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+ach.c.gmc+
                 lrecon_salience.z.gmc+
             (1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod3.ach)
```

### salience moderation

```{r}
mod4.ach<-lmer(lrecon.z~gndr.c.gmc+age10.c.gmc+ach.c.gmc+
                 lrecon_salience.z.gmc+
             ach.c.gmc:lrecon_salience.z.gmc+
             (1|cntry),
           weights = anweight,data=temp.fdat)
getFE(mod4.ach)

emtrends(mod4.ach,
         var="ach.c.gmc",
         specs="lrecon_salience.z.gmc",
         at=list(lrecon_salience.z.gmc=c(-1,0,1)),
         disable.pbkrtest=T,
         lmerTest.limit = 25000,
         infer=c(T,T))

```

### figure data

```{r}
by=0.05

p.ach<-
  emmip(mod4.ach,
        lrecon_salience.z.gmc ~ ach.c.gmc,
        at=list(lrecon_salience.z.gmc = c(-1,0,1),
                ach.c.gmc=
                  seq(from=
                        round(range(temp.fdat$ach.c.gmc)[1],2),
                      to=round(range(temp.fdat$ach.c.gmc)[2],
                               2),by=by)),
        plotit=F,CIs=TRUE,type="response",
        disable.pbkrtest=T,lmerTest.limit=30000)

p.ach$lrecon_salience<-p.ach$tvar

levels(p.ach$lrecon_salience)<-
  c("Low Salience","Average Salience","High Salience")

min.low<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc<=(-1),
                "ach.c.gmc"])
max.low<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc<=(-1),
                "ach.c.gmc"])

p.ach$filter.low<-
  ifelse(p.ach$lrecon_salience.z.gmc==(-1) &
           (p.ach$ach.c.gmc<min.low | 
              p.ach$ach.c.gmc>max.low),0,1)

table(p.ach$filter.low)

min.mid<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc>(-1) |
                  temp.fdat$lrecon_salience.z.gmc<(1),
                "ach.c.gmc"])
max.mid<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc>(-1) |
                  temp.fdat$lrecon_salience.z.gmc<(1),
                "ach.c.gmc"])

p.ach$filter.mid<-
  ifelse(p.ach$lrecon_salience.z.gmc==(0) &
           (p.ach$ach.c.gmc<min.mid | 
              p.ach$ach.c.gmc>max.mid),0,1)

table(p.ach$filter.mid)

min.high<-
  min(temp.fdat[temp.fdat$lrecon_salience.z.gmc>=(1) ,
                "ach.c.gmc"])
max.high<-
  max(temp.fdat[temp.fdat$lrecon_salience.z.gmc>=(1) ,
                "ach.c.gmc"])

p.ach$filter.high<-
  ifelse(p.ach$lrecon_salience.z.gmc==(1) &
           (p.ach$ach.c.gmc<min.high | 
              p.ach$ach.c.gmc>max.high),0,1)

table(p.ach$filter.high)

export(p.ach,overwrite=T,
       "../../results/figures/figdata/ach_ELR_salience.xlsx")

```

# Session info

```{r}
sinf<-sessionInfo()
print(sinf,locale=F)
```