---
title: "ERQ3. Are personal values associated with not having voted in the previous national elections, despite being eligible to vote?"
output: 
  html_document: 
    toc: yes
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Preparations

## Packages

```{r}

library(lme4)
library(lmerTest)
#library(emmeans)
library(r2mlm)
library(rio)
library(dplyr)
library(vjihelpers)
#library(psych)
library(tibble)
```

## Functions

```{r}

source("../custom_functions.R")
```

## Data

```{r}
fdat<-import("../../data/processed/fdat.xlsx")
```

## Variables

```{r}

value.vars<-
  c("con","tra","ben","uni","sdi",
        "sti","hed","ach","pow","sec")

value.vars.c<-paste0(value.vars,".c")


table(fdat$vote)
table(fdat$vote.c)

fdat$vote.DV<-fdat$vote.c+0.5
table(fdat$vote.DV)
```

## Data filtering and centering predictors

```{r}

temp.fdat<- fdat %>% 
    dplyr::select(all_of(value.vars),
                  all_of(value.vars.c),
                  "vote.DV",
                  "gndr.c",
                  "age10.c",
                  "cntry",
                  "anweight") %>%
    na.omit()

temp.fdat<-
    group_mean_center(data=temp.fdat,group.var = "cntry",
                      vars = c(value.vars,
                               value.vars.c,
                               "gndr.c",
                               "age10.c"))

```

# Analysis

## Empty model

```{r}
mod0<-glmer(vote.DV~(1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod0)

```

## Covariate model

```{r}
mod1<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+(1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod1)
```

## All values model

```{r}
mod.all<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  con.gmc+tra.gmc+ben.gmc+uni.gmc+sdi.gmc+
                 sti.gmc+hed.gmc+ach.gmc+pow.gmc+sec.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod.all)

export(rownames_to_column(getFE_glmer(mod.all,p.round = 10,round = 10)),
       "../../results/ERQ3/all_FE.xlsx",overwrite=T)
```

## con

### fixed effect model

```{r}
mod2.con<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  con.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.con)

export(rownames_to_column(getFE_glmer(mod2.con,p.round = 10,round = 10)),
       "../../results/ERQ3/con_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.con<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  con.c.gmc+
                  (con.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.con)

anova(mod2.con,mod3.con)
```


## tra

### fixed effect model

```{r}
mod2.tra<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  tra.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.tra)

export(rownames_to_column(getFE_glmer(mod2.tra,p.round = 10,round = 10)),
       "../../results/ERQ3/tra_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.tra<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  tra.c.gmc+
                  (tra.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.tra)
anova(mod2.tra,mod3.tra)
```




## ben

### fixed effect model

```{r}
mod2.ben<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  ben.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.ben)

export(rownames_to_column(getFE_glmer(mod2.ben,p.round = 10,round = 10)),
       "../../results/ERQ3/ben_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.ben<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  ben.c.gmc+
                  (ben.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.ben)
anova(mod2.ben,mod3.ben)
```

## uni

### fixed effect model

```{r}
mod2.uni<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  uni.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.uni)

export(rownames_to_column(getFE_glmer(mod2.uni,p.round = 10,round = 10)),
       "../../results/ERQ3/uni_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.uni<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  uni.c.gmc+
                  (uni.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.uni)
anova(mod2.uni,mod3.uni)
```

## sdi

### fixed effect model

```{r}
mod2.sdi<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  sdi.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.sdi)

export(rownames_to_column(getFE_glmer(mod2.sdi,p.round = 10,round = 10)),
       "../../results/ERQ3/sdi_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.sdi<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  sdi.c.gmc+
                  (sdi.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.sdi)
anova(mod2.sdi,mod3.sdi)
```

## sti

### fixed effect model

```{r}
mod2.sti<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  sti.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.sti)

export(rownames_to_column(getFE_glmer(mod2.sti,p.round = 10,round = 10)),
       "../../results/ERQ3/sti_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.sti<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  sti.c.gmc+
                  (sti.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.sti)
anova(mod2.sti,mod3.sti)
```

## hed

### fixed effect model

```{r}
mod2.hed<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  hed.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.hed)

export(rownames_to_column(getFE_glmer(mod2.hed,p.round = 10,round = 10)),
       "../../results/ERQ3/hed_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.hed<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  hed.c.gmc+
                  (hed.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.hed)
anova(mod2.hed,mod3.hed)
```

## ach

### fixed effect model

```{r}
mod2.ach<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  ach.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.ach)

export(rownames_to_column(getFE_glmer(mod2.ach,p.round = 10,round = 10)),
       "../../results/ERQ3/ach_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.ach<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  ach.c.gmc+
                  (ach.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.ach)
anova(mod2.ach,mod3.ach)
```

## pow

### fixed effect model

```{r}
mod2.pow<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  pow.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.pow)

export(rownames_to_column(getFE_glmer(mod2.pow,p.round = 10,round = 10)),
       "../../results/ERQ3/pow_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.pow<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  pow.c.gmc+
                  (pow.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.pow)
anova(mod2.pow,mod3.pow)
```

## sec

### fixed effect model

```{r}
mod2.sec<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  sec.c.gmc+
                  (1|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"))
summary(mod2.sec)

export(rownames_to_column(getFE_glmer(mod2.sec,p.round = 10,round = 10)),
       "../../results/ERQ3/sec_FE.xlsx",overwrite=T)
```

### random effect model

```{r}
mod3.sec<-glmer(vote.DV~gndr.c.gmc+age10.c.gmc+
                  sec.c.gmc+
                  (sec.c.gmc|cntry),
           weights = anweight,data=temp.fdat,
           family = binomial(link="logit"),
           control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.sec)
anova(mod2.sec,mod3.sec)
```

# Session info

```{r}
sinf<-sessionInfo()
print(sinf,locale=F)
```